Price of Anarchy for Mean Field Games

### 2018-07-16 PoA.tex
editing second half of proposition 5

\subsection{\textbf{Linear Quadratic Control of McKean-Vlasov Type Involving the Law of the Control}}\label{sec:EMKV}
To solve the linear quadratic optimal control problem of McKean-Vlasov type involving the law of the control (LQEMKV), we begin with the reduced Hamiltonian, which is the same as in the LQEMFG problem:
\begin{equation*}
\begin{split}
    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y\\
    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right).
\end{split}
\end{equation*}
Since we require $\bar{\nu}_t$ to be equal to $\mathbb{E}(\alpha_t)$ throughout the optimization, it is not sufficient to minimize the Hamiltonian with respect to the $\alpha$ input alone in order to guarantee optimality. A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{cite_todo}. Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition is the following:
$\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
\begin{equation*}
    \partial_{\alpha}H(t,X_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\nu}}H(t,\tilde{X}_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),\tilde{Y}_t) \right]=0,
\end{equation*}
where the adjoint equation is given by:
\begin{equation*}
\begin{split}
    dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\
    Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\mu}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
\end{split}
\end{equation*}
and $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$. In the present LQ case, the sufficient condition can be used to solve for:
\begin{equation*}
    \hat{\alpha}_t=a^{MKV}(t)Y_t+b^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
and:
\begin{equation*}
    \mathbb{E}(\hat{\alpha}_t)=c^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
with:
\begin{equation*}
\begin{split}
    a^{MKV}(t)&=-\frac{b_2(t)}{r(t)+\bar{r}(t)} \\
    b^{MKV}(t)&=-\frac{1}{r(t)+\bar{r}(t)}\left(\bar{b}_2(t)-\frac{\bar{r}(t)\bar{s}(t)(\bar{s}(t)-2)(b_2(t)+\bar{b}_2(t))}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2} \right) \\
    c^{MKV}(t)&=-\frac{b_2(t)+\bar{b}_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2}.
\end{split}
\end{equation*}
So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
\begin{equation}
\begin{split}
        dX_t=&\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
        dY_t=&-\left((q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right)dt +Z_t dW_t
\end{split}
\label{eq:FBSDE_EMKV}
\end{equation}
with initial condition $X_0=\xi$, and terminal condition $Y_T=(q_T+\bar{q}_T)X_T+s_T\bar{q}_T(s_T-2)\mathbb{E}X_T$.

@@

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + \zeta^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} } } \nonumber \\
		&=:&\kappa.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
	\end{equation*}
	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

	%---------------------------
	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
	$$
	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$.	 $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$. Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.

@@

	Following the methodology of the proof of Proposition \ref{prop:r_bar_r}, let $\epsilon>0$. Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:\zeta$. We have the following two inequalities for $\bar{b}_2<\bar{b}^*_2$ and $\forall t \in [0,T]$:
		\begin{IEEEeqnarray*}{rl}
			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
			&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
			&< \infty,
		\end{IEEEeqnarray*}
		and 
		\begin{IEEEeqnarray*}{rl}
			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} }\\
			&>  0.
		\end{IEEEeqnarray*}
		Thus, we can deduce that:
		\begin{IEEEeqnarray}{rCl}
			\vert u_t^{\bar{b}_2} \vert  &\leq& \kappa,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
		\end{IEEEeqnarray}
	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2 \to 0}_t$ is uniformly bounded over $t \in [0,T]$ for small enough $\bar{b}_2$.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t.$$
	Moreover, $\bar{x}_t^{\bar{b}_2,MFG}$ is uniformly bounded over $\bar{b}_2<\bar{b}^*_2$ and $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure. Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{\bar{b}_2 \to 0,MFG} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	\begin{equation*}
	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.     
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2 \to 0} > 1. $$

>>>>

\subsection{\textbf{Linear Quadratic Control of McKean-Vlasov Type Involving the Law of the Control}}\label{sec:EMKV}
To solve the linear quadratic optimal control problem of McKean-Vlasov type involving the law of the control (LQEMKV), we begin with the reduced Hamiltonian, which is the same as in the LQEMFG problem:
\begin{equation*}
\begin{split}
    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y\\
    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right).
\end{split}
\end{equation*}
Since we require $\bar{\nu}_t$ to be equal to $\mathbb{E}(\alpha_t)$ throughout the optimization, it is not sufficient to minimize the Hamiltonian with respect to the $\alpha$ input alone in order to guarantee optimality. A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{carmona_acciaio}. Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition is the following:
$\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
\begin{equation*}
    \partial_{\alpha}H(t,X_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\nu}}H(t,\tilde{X}_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),\tilde{Y}_t) \right]=0,
\end{equation*}
where the adjoint equation is given by:
\begin{equation*}
\begin{split}
    dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\
    Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\mu}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
\end{split}
\end{equation*}
and $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$. In the present LQ case, the sufficient condition can be used to solve for:
\begin{equation*}
    \hat{\alpha}_t=a^{MKV}(t)Y_t+b^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
and:
\begin{equation*}
    \mathbb{E}(\hat{\alpha}_t)=c^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
with:
\begin{equation*}
\begin{split}
    a^{MKV}(t)&=-\frac{b_2(t)}{r(t)+\bar{r}(t)} \\
    b^{MKV}(t)&=-\frac{1}{r(t)+\bar{r}(t)}\left(\bar{b}_2(t)-\frac{\bar{r}(t)\bar{s}(t)(\bar{s}(t)-2)(b_2(t)+\bar{b}_2(t))}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2} \right) \\
    c^{MKV}(t)&=-\frac{b_2(t)+\bar{b}_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2}.
\end{split}
\end{equation*}
So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
\begin{equation}
\begin{split}
        dX_t=&\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
        dY_t=&-\left((q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right)dt +Z_t dW_t
\end{split}
\label{eq:FBSDE_EMKV}
\end{equation}
with initial condition $X_0=\xi$, and terminal condition $Y_T=(q_T+\bar{q}_T)X_T+s_T\bar{q}_T(s_T-2)\mathbb{E}X_T$.

@@

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{rl}
		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
		&< \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
		&>  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{IEEEeqnarray}{rCl}
		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
		&=:&c_2.  \nonumber
	\end{IEEEeqnarray}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
	\end{equation*}
	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

	%---------------------------
	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
	$$
	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$.	 $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV,r} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA^r = 1$. Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.

@@

	Following the methodology of the proof of Proposition \ref{prop:r_bar_r}, let $\epsilon>0$. Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$. We have the following two inequalities for $\bar{b}_2<\bar{b}^*_2$ and $\forall t \in [0,T]$:
		\begin{IEEEeqnarray*}{rl}
			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
			&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
			&< \infty,
		\end{IEEEeqnarray*}
		and 
		\begin{IEEEeqnarray*}{rl}
			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
			&>  0.
		\end{IEEEeqnarray*}
		Thus, we can deduce that:
		\begin{IEEEeqnarray}{rCl}
			\vert u_t^{\bar{b}_2} \vert  &\leq& c_2,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
		\end{IEEEeqnarray}
	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2 \to 0}_t$ is uniformly bounded over $t \in [0,T]$ for small enough $\bar{b}_2$.

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t.$$
	Moreover, $\bar{x}_t^{\bar{b}_2,MFG}$ is uniformly bounded over $\bar{b}_2<\bar{b}^*_2$ and $t \in [0,T]$, i.e. 
	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure. Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{\bar{b}_2 \to 0,MFG} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	\begin{equation*}
	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.     
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$
